Backward Population Synthesis: Mapping the Evolutionary History of Gravitational-Wave Progenitors

### 2022-11-26 src/tex/ms.tex
Add validation sentence to line 614

Note that some events did not pass the KL divergence test we proposed in section
\ref{sec:method}; we do not include these systems in figure
\ref{fig:GWTC-3_f_acc_mass}. Binaries that form low-mass compact objects have
lower amounts of fallback and tend to have correspondingly larger variance in
their random natal kicks. Larger kicks can unbind the progenitor binary, or lead
to wide binaries that do not merge within a Hubble time.  In these cases, the
extra variance during the reprojection can produce a posterior that may not
agree with the original posterior, hence yielding a higher KL divergence.

>>>>

\textbf{We have validated the robustness of every events shown in
\ref{fig:GWTC-3_f_acc_mass} by reprojecting the posterior density in the
evolutionary parameter space to the observable space.} Note that some events did
not pass the KL divergence test we proposed in section \ref{sec:method}; we do
not include these systems in figure \ref{fig:GWTC-3_f_acc_mass}. Binaries that
form low-mass compact objects have lower amounts of fallback and tend to have
correspondingly larger variance in their random natal kicks. Larger kicks can
unbind the progenitor binary, or lead to wide binaries that do not merge within
a Hubble time.  In these cases, the extra variance during the reprojection can
produce a posterior that may not agree with the original posterior, hence
yielding a higher KL divergence.
